%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://linkedin.com/in/vazzup}{\Large Vatsal Kanakiya}} & Email : \href{mailto:vatsalkanakiya@gmail.com}{vatsalkanakiya@gmail.com}\\
  \href{http://linkedin.com/in/vazzup}{linkedin.com/in/vazzup} -- \href{http://github.com/vazzup}{github.com/vazzup} -- \href{http://codechef.com/users/vazzup}{codechef.com/users/vazzup} & Mobile : +91-982-137-2343 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {K. J. Somaiya College of Engineering}{Mumbai, India}
      {Bachelor of Technology in Computer Engineering}{Aug. 2014 -- Current}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Morgan Stanley}{Mumbai, India}
      {Summer Technology Analyst}{May 2017 -- July 2017}
      \resumeItemListStart
        \resumeItem{Controller's Workbench}
          {Implemented a unique algorithm to store and retrieve hierarchical data to and from a relational database in a paginated fashion which led to a drastic improvement in the performance of the application under huge stress.}
      \resumeItemListEnd
    \resumeSubheading
      {L. V. Prasad Eye Institute}{Hyderabad, India}
      {LVP-MITRA Research Fellow}{Jan 2014 - Oct 2016}
      \resumeItemListStart
        \resumeItem{Pediatric Perimeter}
          {Worked on the software and hardware of the device}
        \resumeItem{Gaze Tracking}
          {Was mentor of the Gaze Tracking project at the 'Engineering the Eye' Hackathon 2016. Implemented unique Image Processing and Machine Learning algorithms to achieve the same.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXTRACURRICULAR------------
\section{Extra Curricular}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Committee Head, KJSCE Codecell}{Mumbai, India}
      {Led a team of 11 members to conduct various seminars and workshops for fellow students}{July 2016 -- May 2017}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Automated Gait Generation for Simulated Machines{\em (Ongoing)}}
      {L. Y. Project which generates gait for simulated machines with no external input using only Self Modelling and Reinforcement Learning.}
    \resumeSubItem{Controller's Workbench}
      {A visualisation tool for financial data, written in C\#.}
    \resumeSubItem{Pediatric Perimeter}
      {A first of its kind device to measure the visual fields of infants to detect defects and help provide early stage medical aid.}
    \resumeSubItem{TypeRacer Terminal}
      {A terminal application which allows users to practise and improve typing speed and accuracy. Written in Python using the ncurses library.}
    \resumeSubItem{VazzupOJ}
      {A barebones online judge on the lines of SPOJ and OVaOJ.}
  \resumeSubHeadingListEnd
%--------------------------------------

%--------COMPETITIONS------------------
\section{Competitions}
  \resumeSubHeadingListStart
    \resumeSubheading{DJSCE Code Uncode}{Mumbai}{3\textsuperscript{rd}/200 participants}{Feb 2016}
    \resumeSubheading{ACM ICPC Asia Regionals}{Chennai}{73\textsuperscript{rd}/867 teams}{Dec 2016}
    \resumeSubheading{ACM ICPC Asia Regionals}{Amritapuri}{219\textsuperscript{th}/1981 teams}{Dec 2016}
    \resumeSubheading{ACM ICPC Asia Regionals}{Amritapuri}{228\textsuperscript{th}/1572 teams}{Dec 2015}
  \resumeSubHeadingListEnd
%--------------------------------------

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: C / C++, Java, Python3, C\#}
      \hfill
    }
    \vspace{-4pt}
    \item{
      \textbf{Web Technologies}{: HTML / CSS, Javascript, Typescript, PHP, SQL, Angular, Django}
      \hfill
    }
    \vspace{-4pt}
    \item{
      \textbf{ML / DL Frameworks}{: Tensorflow, Keras, Pytorch, Scikit-learn}
      \hfill
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
